---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

runr: a tidy simulation runner
=============================

runr provides an opinionated wrapper to run simulations and recover tidy output.

The packages exports one function, `run`, which runs a function with some
varying parameters, and some fixed parameters. `run`, expects the varying
parameters in a data.frame and the fixed parameters in a list or environment.
It returns the results in an data.frame that can be `cbind`-ed to the input
data.frame.

[![Travis-CI Build Status](https://travis-ci.org/ashander/runr.svg?branch=master)](https://travis-ci.org/ashander/runr)
[![Coverage Status](https://img.shields.io/codecov/c/github/ashander/runr/master.svg)](https://codecov.io/github/ashander/runr?branch=master)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Install
`devtools::install_github('ashander/runr')`

# Example Usage:
```{r, run-ex}
require(devtools)
devtools::run_examples('.')
```

# Details

## Vignette

For further examples, [read the vignette](http://www.ashander.info/runr/doc/debug-profile.html).
It focuses on on debug and profile output.

## Documentation

Better to install the package and do `require(runr); ?run`, but here's an ugly
preview of the help file:

```{r, help}
cat(readLines('man/run.Rd'), sep = '\n')
```

