---
title: "Debugging and Profiling"
author: "Jaime Ashander"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package only provides a single function `run`

```{r, load}
library(runr)
## to see all the code in `run`, uncomment and evaluate
## run
```

Here's the core of run:
```r
require(dplyr)
require(lazyeval)
run <- function(data, fun, fixed_parameters, ...) {
  ## ....
  ## argument checking
  ##

  fixed_parameters <- as.environment(fixed_parameters)
  grouped_out <- do_(rowwise(data), ~ do.call(fun, c(., fixed_parameters, ...)))
  ungroup(grouped_out)
}
```


# Worked example

We start with the example (viewable in the R console with `?run`)

```{r, example}
growth <- function(n, r, K, b) {
  # Ricker-like growth curve in n = log N
  # this is an obviously-inefficient way to do this ;)
  n  + r - exp(n) / K - b - rnorm(1, 0, 0.1)
}
data <- expand.grid(
                    b = seq(0.01, 0.5, length.out=10),
                    K = exp(seq(0.1, 5, length.out=10)),
                    r = seq(0.5, 3.5, length.out=10)
                    )
initial_data = list(N0=0.9, T=5, reps=100)
growth_runner <- function(r, K, b, ic, ...) {
  n0 = ic$N0
  T = ic$T
  reps = ic$reps
  data.frame(n_final = replicate(reps, {for(t in 1:T) {
                                          n0 <- growth(n0, r, K, b)
                                        };
                                        n0})
  )
}
```



## Profiling output

Now, we can examine profile output.

```{r, profile-example}
tmp <- tempfile()
Rprof(tmp, interval = 0.01, line.profiling = TRUE)
output <- run(data, growth_runner, initial_data)
Rprof(NULL)
summaryRprof(tmp)$by.self
```

## Traceback output

To get a look at the call stack, we  replace `growth_runner`, with a function
that intentionally raises an error.

```{r, example-change}
error_runner <- function(r, K, b, ic, ...) {
    stop("thrown an error")
}
```

This way, we can see an example traceback. Note, the code below isn't run in
building the vignette (because it throws and error), but sample output is in
the code block below.

```{r, debug-example, eval=FALSE}
run(data, error_runner, initial_data, error = TRUE)
traceback()
## 15: stop("thrown an error") at #2
## 14: (function (r, K, b, ic, ...)
##          {
## 		         stop("thrown an error")
## 	     })(b = 0.01, K = 1.10517091807565, r = 0.5, <environment>, error = TRUE)
## 13: do.call(fun, c(., fixed_parameters, ...))
## 12: eval(expr, envir, enclos)
## 11: eval(args[[j]]$expr, envir = env)
## 10: do_.rowwise_df(., interp(~do.call(fun, c(., fixed_parameters,
## 					             ...))))
## 9: do_(., interp(~do.call(fun, c(., fixed_parameters, ...))))
## 8: function_list[[i]](value)
## 7: freduce(value, `_function_list`)
## 6: `_fseq`(`_lhs`)
## 5: eval(expr, envir, enclos)
## 4: eval(quote(`_fseq`(`_lhs`)), env, env)
## 3: withVisible(eval(quote(`_fseq`(`_lhs`)), env, env))
## 2: data %>% rowwise %>% do_(interp(~do.call(fun, c(., fixed_parameters,
## 						          ...)))) %>% as.data.frame() at run.r#55
## 1: run(data, error_runner, initial_data, error = TRUE)
```
